Outputs - civil servants' survey

### 2024-12-06 reports/paper_outputs_Dec_2024.qmd
Update paper_outputs_Dec_2024.qmd

exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)

exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)

@@

```{r}
politicization_mod1 <- lm(PROJECT_POLITICIZATION ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist,
            data=data_for_analysis_senior)
politicization_mod1_relig <- politicization_mod1 %>% update(.~.+religiosity)

@@

Model for exit, voice and work
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   
              PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist,
            data=data_for_analysis_senior)
exit_mod1_relig <- exit_mod1 %>% update(.~.+religiosity)

voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
voice_mod1_relig <- voice_mod1 %>% update(.~.+religiosity)

work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
work_mod1_relig <- work_mod1 %>% update(.~.+religiosity)

>>>>

exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)

exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)

@@

```{r}
politicization_mod1 <- lm(PROJECT_POLITICIZATION ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party,
            data=data_for_analysis_senior)
politicization_mod1_relig <- politicization_mod1 %>% update(.~.+religiosity)

@@

Model for exit, voice and work
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   
              PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party,
            data=data_for_analysis_senior)
exit_mod1_relig <- exit_mod1 %>% update(.~.+religiosity)

voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party)
voice_mod1_relig <- voice_mod1 %>% update(.~.+religiosity)

work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT+ education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party)
work_mod1_relig <- work_mod1 %>% update(.~.+religiosity)
